% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Rafael Contreras Rodriguez}

\basicInfo{
  \email{raf@contrer.as} \textperiodcentered\ 
  \phone{021525788} \textperiodcentered\ 
  \linkedin[rafcontreras]{https://www.linkedin.com/in/rafcontreras}}

\section{\\ COVER LETTER}
  \role{}{}
  18 August 2017\par
  IAG NZ\par
  ~\par
  I am convinced that I am one of the self-motivated Front-End Developers that you seek. As a UX Architect with multiple platform experience and strong project management skills, I am confident that I would make a succesful addition to the iMonitor team as your new Front-End Developer.
  \par

\section{\\ Why me}
  \role{}{}
  I am passionate for a high quality UX/UI product that meets the needs of the end user, achieves business goals and encourages the participation of the development team.\par
  ~\par
  I have a strong sense of empathy that has given me the ability to learn what the users need, what the users want, and the capacity to differentiate between them. That way I can deliver the right tool for the right solution.\par
  ~\par
  I have more than twenty years of experience in the Information Technology sector with a variety of roles and projects that have increased my knowledge and understanding of all areas of a business.\par

\section{\\ My values}
  \role{}{}
  I believe in human equality, the ethical treatment of animals, and the responsible care of our environment.\par
  ~\par
  I do not have a religion but I respect other people's beliefs and acknowledge the power of faith.\par
  ~\par
  Everyday I make the conscious effort to treat people with kindness.\par

\section{\\ About me}
  \role{}{}
  I am a Mexican living in New Zealand for the past 8 and a half years, I have a little dog named {Taco} whom I love. I enjoy science fiction books, movies and TV shows. My latest hobby is cooking and I enjoy it very much.\par
  ~\par

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
