% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Rafael Contreras Rodriguez}

\basicInfo{
  \email{raf@contrer.as} \textperiodcentered\ 
  \phone{021525788} \textperiodcentered\ 
  \linkedin[rafcontreras]{https://www.linkedin.com/in/rafcontreras}}

\section{\faUser\ Summary}
  \begin{itemize}
    \item 8+ years experience hands-on work and leading strategy and production of tidy, thorough UX deliverables and best practices:
    \begin{itemize}
      \item Site maps, process flows, wireframes, functional specifications
      \item Lead user discovery and stakeholder workshops
      \item Usability testing
      \item Google analytics tagging and post-launch analysis
    \end{itemize}
    \item History of pleasant and effective team leadership working with UX people, visual designers, developers, executives, stakeholders, clients and end users.
    \item My specialty and preference is for large, complex projects.
    \item Enough of a working familiarity of HTML5, CSS3, Javascript, Java, .NET, PHP, Git and versioning to converse with developers about plans, progress and launches; I especially like working with developers and engineers since I started as one.
    \item I energetically think on my feet to keep coming up with new ideas if old ones aren’t working; Flexible enough to know when something isn’t working and tactfully lobby for the best solution.
    \item Daily, I keep up on current important ideas in UX, front-end development, visual design, and technology arts and sciences.
  \end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Bayleys Realty Group} Auckland, New Zealand}{Aug 2015 -- Present}
\role{User Experience Architect}{}
  At Bayleys Real Estate I am responsible of the User Experience research, User Interface design, and front-end development and testing for the various internal and public facing digital services and websites.\par
  ~\par
  {The role:}\par
  ~\par
  Creating Mobile, Tablet and Web based, user centric wireframes for Real Estate domain, organizing workshop with cross domain business teams, coordinating projects in prototype cycles between development and business. Further responsibilities include, keeping brand language consistent, keeping UX between various user journeys seamless for the end user and managing multiple projects at various stages of the design cycles and development timelines.\par
  ~\par
  {Achievements:}\par
  ~\par
  \begin{itemize}
    \item Increased daily page visits by \~580\% compared to 2015 \textit{(Source: Google Analytics)}
    \item Achieved second most visited real estate site by daily page visits from fourth since 2015 \textit{(Source: similarweb.com as of 28 Nov 2016)}
  \end{itemize}
\datedsubsection{\textbf{Mako Networks} Auckland, New Zealand}{Feb 2012 -- Jul 2015}
\role{User Experience Architect}{}
  As the UX architect I was in charge of the whole digital product experience ranging from marketing website, sales portals and the Mako Central Management System.\par
  ~\par
  {The role:}\par
  ~\par
  Designing and prototyping interfaces for a large scale SAAS solution. Conducting weekly workshops (per project) with developers, stakeholders, clients and end-users. Evangelization about the importance of best practices and user/customer experience.\par
  ~\par
  {Achievements:}\par

\begin{itemize}
  \item Created an unified interface across all digital solutions and products, critically reducing the design / prototyping / development / testing process.
  \item Improved overall performance of the service as it moved from complete server rendering to a combination of client side and backend business logic.
\end{itemize}
\datedsubsection{\textbf{Massimo International} Auckland, New Zealand}{Oct 2008 -- Jan 2012}
\role{Web designer - POS administrator}{}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{ Universidad TecMilenio}, Mexico, Mexico}{2006 -- 2008}
\textit{Masters} in Business Administration
\datedsubsection{\textbf{UNITEC}, Mexico, Mexico}{2002 -- 2005}
\textit{Bachelor} in Graphic Design
\datedsubsection{\textbf{Tec de Monterrey}, Mexico, Mexico}{1998 -- 2002}
\textit{Bachelor} in Computer Science Engineering

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item UI design tools: Adobe Photoshop and Illustrator, Sketch
  \item UX Prototyping tools: Invision, FramerJS, Adobe AfterEffects
  \item Development languages: HTML5, CSS3, JS (jQuery, Node, Angular), PHP, Java, and .Net. Currently learning React and React Native.
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Website: https://contrer.as
  \item GitHub: https://github.com/rafcontreras
  \item Languages: English - Fluent, Spanish - Native speaker, French - Basic
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
